\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-26 papers/itsc_2012/peter-submitted.tex
added peter's comments on the current submitted version

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation
of the real world in a few minutes. AORTA is available open-source and is
easily extensible\footnote{Code available at
\texttt{http://code.google.com/p/road-rage}}, making it easier for users to
test out a number of agent behaviors and intersection policies in a short
time span.

@@

AORTA is divided into three modular components: the map model, micro-simulation
engine, and user interface (UI). The map model transforms OSM maps into AORTA
graphs, then answers pathfinding and geometry queries. The simulation engine
adds a notion of agents, vehicle dynamics, and collisions. Finally, the UI
interactively renders the map and agents. A headless mode also exists to run
experiments without the overhead of visualization. The interaction between
modules is visualized in figure \ref{fig:arch}.

@@

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining
the center line that divides the road into two directions of travel. AORTA
interprets these points as straight lines and projects parallel lanes out using
a fixed width. Turns are modeled with a single straight line connecting the end
of one lane to the start of another.

@@

The builder works incrementally while parsing OSM graphs into the map model,
with each pass feeding the next. The map model is then stored in an XML format.
\begin{enumerate}
  \item OSM encodes many paths besides drivable roads, so the builder first filters
        these out. Next, the builder marks OSM nodes common to multiple roads, since
        they implicitly indicate intersections. Overpasses do not share nodes
        with the roads they cross \cite{osmOverpass}.
  \item OSM \emph{ways} (sequences of nodes) include many
        intersections, so the builder next splits ways into undirected
        segments of roads between exactly two intersections.
  \item The builder multiplies undirected roads into directed lanes in each
        direction (unless the road is marked one-way). The builder guesses the
        number of lanes based on OSM's ``road type'' tag or an explicit number of
        lanes, when that data is available.
  \item The builder constructs turns between incoming and outgoing lanes at each
        intersection. The angle between the two lanes determines whether the turn is
        a left, right, straight, or U-turn. When several lanes all cross into fewer
        lanes, the builder forces merging at the rightmost lanes. 
  \item Because turns are heuristically placed, the graph is often disconnected.
        In order to ensure that an agent will be able to reach any point in the map,
        the builder removes all but the largest strongly connected component of the
        directed graph. Disconnected lanes are spliced out of larger roads, leaving
        geometric gaps, but correctly ensuring connectivity.
\end{enumerate}

@@

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. There are many circumstances where AORTA
simulates one intersection as several in close proximity because roads do not
geometrically line up, but functionally they do. If OSM encoded this data, the
the realism of the simulation would improve. Other simulators have identified
similar issues before \cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

@@

@@

Currently agents cannot change lanes. This causes a second issue: gridlock.
Each agent maintains a safe following distance from the next. If a lane is
filled, then an agent may be forced to stop in an intersection mid-turn and
block other traffic. The default behavior prevents this by refusing to start a
turn before the lookahead engine guarantees no agent will trigger a premature
stop.

@@

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around intersections such as those pictured
in figure \ref{fig:gridlock} in order to enter a lane adjacent to their original
lane.  Since these routes are still legal, it is desirable to prevent or mend
this problem without forcing different routes. However, choosing alternative
moves (by changing lanes or rerouting) is an important constituent of a
sufficient condition for the liveness of a road network \cite{AAAI11-au}.

@@

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on configurability. In conjunction with Open Street Maps, AORTA
allows users to repeat an experiment in different places with minimal effort.
Future work will exploit the flexible infrastructure of interactions between
agent behaviors and intersections by exploring dynamic replanning and adaptable
signal timings. On top of these structures, applications could experiment with
ideas such dynamic contra-flow \cite{ITSC11-hausknecht}.  There will also be an
effort to improve AORTA as a framework by including a lane-changing model,
preventing gridlock, and supporting more agents through parallel computing.

>>>>

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation
of the real world in a few minutes. AORTA is available open-source and is
easily extensible\footnote{Code available at
\texttt{http://code.google.com/p/road-rage}}, making it easier\commentp{easier
is a comparitive word, so this should be either "easy" or "easier than...."}
for users to test out a number of agent behaviors and intersection policies in
a short time span.

@@

AORTA is divided into three modular components: the map model, micro-simulation
engine, and user interface (UI). The map model transforms OSM maps into AORTA
graphs, then answers pathfinding and geometry queries. The simulation engine
adds a notion of agents, vehicle dynamics, and collisions. Finally, the UI
interactively renders the map and agents. A headless mode also exists to run
experiments without the overhead of visualization. The interaction between
modules is visualized in \commentp{all figure and section references should
have capital F and S respectively}\commentpk{I tend to use Fig.}figure
\ref{fig:arch}.

@@

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining
the center line that divides the road into two directions of travel. AORTA
interprets these points as straight lines \commentp{line segments instead of
lines} and projects parallel lanes out using a fixed width. Turns are modeled
\commentp{approximated} with a single straight line \commentp{segment}
connecting the end of one lane to the start of another.

@@

The builder works incrementally while parsing OSM graphs into the map model,
with each pass feeding the next. The map model is then stored in an XML format.
\begin{enumerate}
  \item OSM encodes many paths besides drivable roads, so the builder first filters
        these out. Next, the builder marks OSM nodes common to multiple roads, since
        they implicitly indicate intersections. Overpasses do not share nodes
        with the roads they cross \cite{osmOverpass}.
  \item OSM \emph{ways} (sequences of nodes) include many
        intersections, so the builder next splits ways into undirected
        segments of roads between exactly two intersections.
  \item The builder multiplies undirected roads into directed lanes in each
        direction (unless the road is marked one-way). The builder guesses the
        number of lanes based on OSM's ``road type'' tag or an explicit number of
        lanes, when that data is available.
  \item The builder constructs turns between incoming and outgoing lanes at each
        intersection. The angle between the two lanes determines whether the turn is
        a left, right, straight, or U-turn. When several lanes all cross into fewer
        lanes, the builder forces merging at the rightmost lanes. 
  \item Because turns are heuristically placed, the graph is often disconnected.
        In order to ensure that an agent will be able to reach any point in the map,
        the builder removes all but the largest strongly connected component of the
        directed graph. Disconnected lanes are spliced out of larger roads, leaving
        geometric gaps, but correctly ensuring connectivity. \commentp{This paragraph was generally unclear, and makes it sound like you are removing huge chunks of the graph}
\end{enumerate}

@@

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns
at each intersection often misses common features like right turn-only lanes
and shared center left turn lanes. There are many circumstances where AORTA
simulates one intersection \commentp{makes it sound like aorta's fault} as
several in close proximity because roads do not geometrically line up, but
functionally they do. If OSM encoded this data, the the\commentp{extra the}
realism of the simulation would improve. Other simulators have identified
\commentp{"dealt with" instead of "identified"} similar issues before
\cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

@@

\commentp{The images in this section need better labels, plus maybe print
better in black and white. For instance, the gridlock issue - since b/w does
not show red explicitly, maybe you should mark the loop in the image. In Fig
3a) the green arrowhead is hidden etc.}

@@

Currently agents cannot change lanes. This causes a second \commentp{potential}
issue: gridlock.  Each agent maintains a safe following distance from the next.
If a lane is filled, then an agent may be forced to stop in an intersection
mid-turn and block other traffic. The default behavior prevents this by
refusing to start a turn before the lookahead engine guarantees no agent will
trigger a premature stop.

@@

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around intersections such as those pictured
in figure \ref{fig:gridlock} in order to enter a lane adjacent to their
original lane.  Since these routes are still legal, it is desirable to prevent
or mend this problem without forcing different routes \commentp{the need for
forccing alternate routes could be clearer}. However, choosing alternative
moves (by changing lanes or rerouting) is an important constituent of a
sufficient condition for the liveness of a road network \cite{AAAI11-au}.

@@

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on configurability. In conjunction with Open Street Maps, AORTA
allows users to repeat an experiment in different places with minimal effort.
Future work will exploit the flexible infrastructure of interactions between
agent behaviors and intersections by exploring dynamic replanning and adaptable
signal timings. On top of these structures, applications could experiment with
ideas such \commentp{as} dynamic contra-flow \cite{ITSC11-hausknecht}.  There
will also be an effort to improve AORTA as a framework by including a
lane-changing model, preventing gridlock, and supporting more agents through
parallel computing.
